Supplementary Information for: Crosslinguistic Word Orders Enable an Efficient Tradeoff between Memory and Surprisal

### 2020-03-29 writeup/si.tex

\begin{figure}
	\begin{center}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byPhonemes-it.pdf}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byPhonemes-memsurp.pdf}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byPhonemes-auc-hist.pdf}
\end{center}
	\caption{Japanese verb suffixes, measuring prediction on the level of phonemes, for real (blue), random (green), and approximately optimized (red) orderings. Left: $I_t$ as a function of $t$. Center: Memory-surprisal tradeoff. Right: Areas under the curve for the memory-surprisal tradeoff.}\label{fig:jap-phon}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byMorphemes-it.pdf}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byMorphemes-memsurp.pdf}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byMorphemes-auc-hist.pdf}
\end{center}
	\caption{Japanese verb suffixes, measuring prediction on the level of morphemes, for real (blue), random (green), and approximately optimized (red) orderings. Left: $I_t$ as a function of $t$. Center: Memory-surprisal tradeoff. Right: Areas under the curve for the memory-surprisal tradeoff.}\label{fig:jap-morph}
\end{figure}

>>>>

\begin{figure}
	\begin{center}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byPhonemes-it.pdf}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byPhonemes-memsurp.pdf}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byPhonemes-auc-hist.pdf}

		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byPhonemes-it-heldout.pdf}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byPhonemes-memsurp-heldout.pdf}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byPhonemes-auc-hist-heldout.pdf}
\end{center}
	\caption{Japanese verb suffixes, measuring prediction on the level of phonemes, for real (blue), random (green), and approximately optimized (red) orderings. Left: $I_t$ as a function of $t$. Center: Memory-surprisal tradeoff. Right: Areas under the curve for the memory-surprisal tradeoff.}\label{fig:jap-phon}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byMorphemes-it.pdf}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byMorphemes-memsurp.pdf}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byMorphemes-auc-hist.pdf}

		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byMorphemes-it-heldout.pdf}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byMorphemes-memsurp-heldout.pdf}
		\includegraphics[width=0.3\textwidth]{../code/ngram-control/create_models_ngrams/morph/Japanese/tradeoffs/figures/Japanese-suffixes-byMorphemes-auc-hist-heldout.pdf}
\end{center}
	\caption{Japanese verb suffixes, measuring prediction on the level of morphemes, for real (blue), random (green), and approximately optimized (red) orderings. Left: $I_t$ as a function of $t$. Center: Memory-surprisal tradeoff. Right: Areas under the curve for the memory-surprisal tradeoff. Top: Simple estimator, Bottom: Heldout estimator}\label{fig:jap-morph}
\end{figure}
